---
title: "<b>What will I earn? An interactive tool for UC grad students to figure out bargaining scenarios</b>"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    navbar: 
      - icon: fa-github fa-lg
        href: http://github.com/liza-wood
    source_code: embed
    theme: 
      version: 4
      bg: "#D3D3D3" 
      fg: "#000000" 
      primary: "#8B0000"
      navbar-bg: "#8B0000"
    
runtime: shiny
---

```{r global, include=FALSE}
library(gsheet)
library(stringr)
library(tidyverse)
library(flexdashboard)

asedec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1uDKy5bVJ785XHanbRuW22U_9XjkOxPg5NIVxTbenLus/edit#gid=970994158")
gsr1_4dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=1978421261")
gsr5dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=590276086")
gsr6dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=1793117733")
gsr7dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=564163227")
gsr8dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=719917995")
gsr9_10dec2 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=143970143")

asedec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Cnhn7i0oIj-97ClEAaK5GcA-8CbrdrFmymDF0FNvYO0/edit#gid=0")
gsr1_4dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=0")
gsr5dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=581919688")
gsr6dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=1969056861")
gsr7dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=1778002963")
gsr8dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=138349835")
gsr9_10dec16 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=959049112")

current_pay <- data.frame(
  "time" = rep("current", 30),
  "step" = rep(1:10, each = 3),
  "yrs_exp_gsr" = rep(c("0-3", "4-6", "7+"), 10),
  "yrs_exp_ta" = rep(c("0-3", "4-6", "7+"), 10),
  "gsr" = rep(c(3667.58, 3952.92, 4383.67, 4734.83, 5049.92 ,
            5384.33, 5707.67, 6161.75, 6656.08, 7186.58)/2, each = 3),
  "ta" = rep(5156.89/2, 30))

current_pay2324 <- current_pay %>% 
  mutate(gsr = gsr,#+(gsr*.02),
         ta = ta,#+(ta*.02),
         time = "2324")
#current_pay2425 <- current_pay2324 %>% 
#  mutate(gsr = gsr+(gsr*.02),
#         ta = ta+(ta*.02),
#         time = "2425")

current_pay <- rbind(current_pay, current_pay2324)

proposed_paydec2 <- data.frame(
  "time" = rep("current", 30),
  "step" = rep(1:10, each = 3),
  "yrs_exp_gsr" = rep(c("0-3", "4-6", "7+"), 10),
  "yrs_exp_ta" = rep(c("0-3", "4-6", "7+"), 10),
  "gsr" = as.numeric(trimws(str_remove_all(c(rep(gsr1_4dec2[13,2], 4*3), 
            rep(c(gsr5dec2[13,2], gsr6dec2[13,2], gsr7dec2[13,2], gsr8dec2[13,2]), each = 3),
            rep(gsr9_10dec2[13,2], 2*3)), "\\$|,"))),
  "ta" = as.numeric(trimws(str_remove_all(asedec2[4,2], "\\$|,"))))

proposed_pay2324dec2 <- data.frame(
  "time" = rep("2324", 30),
  "step" = rep(1:10, each = 3),
  "yrs_exp_gsr" = rep(c("0-3", "4-6", "7+"), 10),
  "yrs_exp_ta" = rep(c("0-3", "4-6", "7+"), 10),
  "gsr" = as.numeric(trimws(str_remove_all(c(rep(c(gsr1_4dec2[14,2], gsr1_4dec2[14,3],gsr1_4dec2[14,4]), 4), 
            c(gsr5dec2[14,2], gsr5dec2[14,3], gsr5dec2[14,4], 
              gsr6dec2[14,2], gsr6dec2[14,3], gsr6dec2[14,4], 
              gsr7dec2[14,2], gsr7dec2[14,3], gsr7dec2[14,4], 
              gsr8dec2[14,2], gsr8dec2[14,3], gsr8dec2[14,4]),
            rep(c(gsr9_10dec2[14,2],gsr9_10dec2[14,3],gsr9_10dec2[14,4]), 2)), "\\$|,"))),
  "ta" = as.numeric(trimws(str_remove_all(c(asedec2[5,2],asedec2[5,3],asedec2[5,4]), "\\$|,"))))

proposed_paydec2 <- rbind(proposed_paydec2, proposed_pay2324dec2)

proposed_paydec16 <- data.frame(
  "time" = rep("current", 30),
  "step" = rep(1:10, each = 3),
  "yrs_exp_gsr" = rep(c("0-3", "4-6", "7+"), 10),
  "yrs_exp_ta" = rep(c("0-3", "4-6", "7+"), 10),
  "gsr" = as.numeric(trimws(str_remove_all(c(rep(gsr1_4dec16[13,2], 4*3), 
            rep(c(gsr5dec16[13,2], gsr6dec16[13,2], gsr7dec16[13,2], gsr8dec16[13,2]), each = 3),
            rep(gsr9_10dec16[13,2], 2*3)), "\\$|,"))),
  "ta" = as.numeric(trimws(str_remove_all(asedec16[4,2], "\\$|,"))))

proposed_pay2324dec16 <- data.frame(
  "time" = rep("2324", 30),
  "step" = rep(1:10, each = 3),
  "yrs_exp_gsr" = rep(c("0-3", "4-6", "7+"), 10),
  "yrs_exp_ta" = rep(c("0-3", "4-6", "7+"), 10),
  "gsr" = as.numeric(trimws(str_remove_all(c(rep(c(gsr1_4dec16[14,2], gsr1_4dec16[14,3],gsr1_4dec16[14,4]), 4), 
            c(gsr5dec16[14,2], gsr5dec16[14,3], gsr5dec16[14,4], 
              gsr6dec16[14,2], gsr6dec16[14,3], gsr6dec16[14,4], 
              gsr7dec16[14,2], gsr7dec16[14,3], gsr7dec16[14,4], 
              gsr8dec16[14,2], gsr8dec16[14,3], gsr8dec16[14,4]),
            rep(c(gsr9_10dec16[14,2],gsr9_10dec16[14,3],gsr9_10dec16[14,4]), 2)), "\\$|,"))),
  "ta" = as.numeric(trimws(str_remove_all(c(asedec16[5,2],asedec16[5,3],asedec16[5,4]), "\\$|,"))))

proposed_paydec16 <- rbind(proposed_paydec16, proposed_pay2324dec16)
```

```{r function for current pay data}
input_current_data <- function(input){
  if(input$spring == "TA"){
    spring <- current_pay %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$spring == "GSR"){
    spring <- current_pay %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {spring <- 0}


  if(input$summer == "TA"){
    summer <- current_pay %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$summer == "GSR"){
    summer <- current_pay %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {summer <- 0}

  if(input$fall == "TA"){
    fall <- current_pay %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$fall == "GSR"){
    fall <- current_pay %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {fall <- 0}

  if(input$winter == "TA"){
    winter <- current_pay %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$winter == "GSR"){
    winter <- current_pay %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {winter <- 0}

current_df <- data.frame(
  "date" = lubridate::mdy(c("04/01/23", "05/01/23","06/01/23","07/01/23","08/01/23",
                            "09/01/23","10/01/23","11/01/23", "12/01/23", "01/01/24",
                            "02/01/24", "03/01/24")),
  "pay" = rep(c(round(spring[[1]]), round(summer[[1]]), 
                round(fall[[1]]),round(winter[[1]])), each = 3))
return(current_df)
}
```

```{r function for proposed pay data}
input_proposed_datadec2 <- function(input){
  if(input$spring == "TA"){
    springp <- proposed_paydec2 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$spring == "GSR"){
    springp <- proposed_paydec2 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {springp <- 0}

  if(input$summer == "TA"){
    summerp <- proposed_paydec2 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$summer == "GSR"){
    summerp <- proposed_paydec2 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {summerp <- 333}

  if(input$fall == "TA"){
    fallp <- proposed_paydec2 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$fall == "GSR"){
    fallp <- proposed_paydec2 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {fallp <- 0}

  if(input$winter == "TA"){
    winterp <- proposed_paydec2 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$winter == "GSR"){
    winterp <- proposed_paydec2 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {winterp <- 0}

proposed_df <- data.frame(
  "date" = lubridate::mdy(c("04/01/23", "05/01/23","06/01/23","07/01/23","08/01/23",
                            "09/01/23","10/01/23","11/01/23", "12/01/23", "01/01/24",
                            "02/01/24", "03/01/24")),
  "pay" = rep(c(springp[[1]], summerp[[1]], fallp[[1]], winterp[[1]]), each = 3))
return(proposed_df)
}

input_proposed_datadec16 <- function(input){
  if(input$spring == "TA"){
    springp <- proposed_paydec16 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$spring == "GSR"){
    springp <- proposed_paydec16 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {springp <- 0}

  if(input$summer == "TA"){
    summerp <- proposed_paydec16 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "current",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$summer == "GSR"){
    summerp <- proposed_paydec16 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "current",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {summerp <- 333}

  if(input$fall == "TA"){
    fallp <- proposed_paydec16 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$fall == "GSR"){
    fallp <- proposed_paydec16 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {fallp <- 0}

  if(input$winter == "TA"){
    winterp <- proposed_paydec16 %>% 
      select(-c(gsr, yrs_exp_gsr, step)) %>% 
      filter(time == "2324",
             yrs_exp_ta == input$yrs_exp_ta) %>% 
      unique() %>% 
      select(ta)
  } else if(input$winter == "GSR"){
    winterp <- proposed_paydec16 %>% 
      select(-c(ta, yrs_exp_ta)) %>% 
      filter(time == "2324",
             step == input$step,
             yrs_exp_gsr == input$yrs_exp_gsr) %>% 
      unique() %>% 
      select(gsr)
  } else {winterp <- 0}

proposed_df <- data.frame(
  "date" = lubridate::mdy(c("04/01/23", "05/01/23","06/01/23","07/01/23","08/01/23",
                            "09/01/23","10/01/23","11/01/23", "12/01/23", "01/01/24",
                            "02/01/24", "03/01/24")),
  "pay" = rep(c(springp[[1]], summerp[[1]], fallp[[1]], winterp[[1]]), each = 3))
return(proposed_df)
}
```

Column {.sidebar}
=============================================

Adjust the following scenarios for your upcoming employment plans. 

<font size="2em">
What kinds of employment will you have each quarter?  

```{r seasonal selectors}
selectInput('spring', 'Spring 2023:', c("TA", "GSR", "None"), selected= "GSR")
selectInput('summer', 'Summer 2023:', c("TA", "GSR", "None"), selected= "GSR")
selectInput('fall', 'Fall 2023:', c("TA", "GSR", "None"), selected= "TA")
selectInput('winter', 'Winter 2024:', c("TA", "GSR", "None"), selected= "GSR")
```

If GSR, what step do you expect to be hired at? 
```{r step selectors}
numericInput('step', '', 3,
              min = 1, max = 10)
```

How many quarters of experience do you have?

```{r experience selectors}
selectInput('yrs_exp_gsr', 'GSR:', c("0-3", "4-6", "7+"), selected= "1")
selectInput('yrs_exp_ta', 'TA:', c("0-3", "4-6", "7+"), selected= "1")
```
</font>

Dec 16 Offer {data-navmenu="Calculator"} 
=======================================================================

Row {data-height=100}
-------------------------------------

### 
<font size="4em" color="#5A5A5A">
```{r, echo=FALSE}
textOutput("text")
```
</font>
```{r, context="server"}
output$text <- renderText({
  current_df <- input_current_data(input)
  paste("Current annual gross: $ ",round(sum(current_df$pay))) })
```

### 
<font size="4em" color="#152388">
```{r, echo=FALSE}
textOutput("text2")
```
</font>
```{r, context="server"}
output$text2 <- renderText({
  proposed_df16 <- input_proposed_datadec16(input)
  paste("Proposed annual gross: $ ",round(sum(proposed_df16$pay))) })
```

### 
<font size="4em" color="#8B0000">
```{r, echo=FALSE}
textOutput("text3")
```
</font>
```{r, context="server"}
output$text3 <- renderText({
  proposed_df16 <- input_proposed_datadec16(input)
  current_df <- input_current_data(input)
  paste("Annual pay difference:
        $ ", round(sum(proposed_df16$pay)) - round(sum(current_df$pay))) })
```

### 
<font size="4em" color="#023020">
```{r, echo=FALSE}
textOutput("text4")
```
</font>
```{r, context="server"}
output$text4 <- renderText({
  proposed_df16 <- input_proposed_datadec16(input)
  current_df <- input_current_data(input)
  paste("Raise:", 
        100*(round(sum(proposed_df16$pay)/sum(current_df$pay), 2)-1), "%") })
```

Row 
-------------------------------------
### 

```{r current pay plot Dec 16}
renderPlot({
  current_df <- input_current_data(input)
 p <- ggplot(current_df, aes(x = date, y = pay, label = paste0("$", pay))) +
    geom_line(color = "#D3D3D3") +
    geom_point() +
    geom_text(vjust = -1) +
    ylim(c(0,4600)) +
    theme_minimal() +
    theme_strike() +
   labs(title = "Current UC pay scale", y = "Gross monthly pay ($)", x = "",
        caption = "Note: These pay scale data remain unchanged from the 2021-22 academic year")

 print(p)
})
```

Row 
-------------------------------------
###

```{r proposed pay plot Dec 16}
renderPlot({
  proposed_df <- input_proposed_datadec16(input)
  p <- ggplot(proposed_df, aes(x = date, y = pay, label = paste0("$", pay))) +
    geom_line(color = "#D3D3D3") +
    geom_point() +
    geom_text(vjust = -1) +
    ylim(c(0,4600)) +
    theme_minimal() +
    theme_strike() +
   labs(title = "Pay scale proposed by the UC's Dec 16. offer", y = "Gross monthly pay ($)", x = "")
  print(p)
})
```

Dec 2 Offer {data-navmenu="Calculator"} 
=======================================================================

Row {data-height=100}
-------------------------------------

### 
<font size="4em" color="#5A5A5A">
```{r, echo=FALSE}
textOutput("text5")
```
</font>
```{r, context="server"}
output$text5 <- renderText({
  current_df <- input_current_data(input)
  paste("Current annual gross: $ ",round(sum(current_df$pay))) })
```

### 
<font size="4em" color="#152388">
```{r, echo=FALSE}
textOutput("text6")
```
</font>
```{r, context="server"}
output$text6 <- renderText({
  proposed_df <- input_proposed_datadec2(input)
  paste("Proposed annual gross: $ ",round(sum(proposed_df$pay))) })
```

### 
<font size="4em" color="#8B0000">
```{r, echo=FALSE}
textOutput("text7")
```
</font>
```{r, context="server"}
output$text7 <- renderText({
  proposed_df <- input_proposed_datadec2(input)
  current_df <- input_current_data(input)
  paste("Annual pay difference:
        $ ", round(sum(proposed_df$pay)) - round(sum(current_df$pay))) })
```

### 
<font size="4em" color="#023020">
```{r, echo=FALSE}
textOutput("text8")
```
</font>
```{r, context="server"}
output$text8 <- renderText({
  proposed_df <- input_proposed_datadec2(input)
  current_df <- input_current_data(input)
  paste("Raise:", 
        100*(round(sum(proposed_df$pay)/sum(current_df$pay), 2)-1), "%") })
```

Row 
-------------------------------------
### 

```{r current pay plot Dec 2}
renderPlot({
  current_df <- input_current_data(input)
 p <- ggplot(current_df, aes(x = date, y = pay, label = paste0("$", pay))) +
    geom_line(color = "#D3D3D3") +
    geom_point() +
    geom_text(vjust = -1) +
    ylim(c(0,4600)) +
    theme_minimal() +
    theme_strike() +
   labs(title = "Current UC pay scale", y = "Gross monthly pay ($)", x = "",
        caption = "Note: These pay scale data remain unchanged from the 2021-22 academic year")

 print(p)
})
```

Row 
-------------------------------------
###


```{r proposed pay plot Dec 2}
renderPlot({
  proposed_df <- input_proposed_datadec2(input)
  p <- ggplot(proposed_df, aes(x = date, y = pay, label = paste0("$", pay))) +
    geom_line(color = "#D3D3D3") +
    geom_point() +
    geom_text(vjust = -1) +
    ylim(c(0,4600)) +
    theme_minimal() +
    theme_strike() +
   labs(title = "Pay scale proposed by the UC's Dec 2. offer", y = "Gross monthly pay ($)", x = "")
  print(p)
})
```

```{r}
theme_strike <- function(base_size = 18, 
                            dark_text = "#1A242F") {
  
  mid_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[2]
  light_text <-  monochromeR::generate_palette(dark_text, "go_lighter", n_colours = 5)[3]
  
  theme_minimal(base_size = base_size) +
    theme(text = element_text(colour = mid_text, family = "Arial", lineheight = 1.1),
          plot.title = element_text(colour = dark_text, family = "Arial", 
                                    size = rel(1.25), margin = margin(12, 0, 8, 0)),
          plot.subtitle = element_text(size = rel(1), margin = margin(0, 0, 0, 0)),
          axis.text.y = element_text(colour = light_text, size = rel(0.9)),
          axis.title.y = element_text(size = rel(0.9), margin = margin(0, 4, 0, 0)),
          axis.text.x = element_text(colour = mid_text, size = rel(.9)),
          #axis.title.x = element_blank(),
          legend.position = "bottom",
          #legend.justification = 1,
          legend.text = element_text(size = rel(.75), margin = margin(0, 0, 0, 0)),
          panel.grid = element_line(colour = "#F3F4F5"),
          plot.caption = element_text(size = rel(0.65), margin = margin(8, 0, 0, 0)),
          plot.margin = margin(0.5, 0.5, 0.5, 0.5,"cm"))
}
```

Information  
=======================================================================

Row {data-height=450}
-------------------------------------
### Data:

Data for the December 2 proposals were taken from Google sheets shared by the UC Bargaining Team.   

* [ASE (Teaching Assistant) spreadsheet (Dec 2)](https://docs.google.com/spreadsheets/d/1uDKy5bVJ785XHanbRuW22U_9XjkOxPg5NIVxTbenLus/edit#gid=970994158)  
* [SRU (GSR) spreadsheet (Dec 2)](https://docs.google.com/spreadsheets/d/1s5c3epn1TOlBz1HzDglZVdpK1DQJj3aLsO3goKMIdDA/edit#gid=143970143)   

Data for the December 16 proposals were taken from the Bargaining Team's [written summary for SRUs](https://docs.google.com/document/d/1IngZvywom_xRZcMg3-Sr1TSOh-GFFd3C80OM5aROyjw/edit) and the [UC's spreadsheet for ASE pay](https://docs.google.com/spreadsheets/d/1yw3tehPnOz6girjThLt7CTJAqyLOA8LF/edit?rtpof=true&sd=true#gid=897821721), and converted into equivalent spreadsheets from Dec 2:  

* [ASE (Teaching Assistant) spreadsheet (Dec 16)](https://docs.google.com/spreadsheets/d/1Cnhn7i0oIj-97ClEAaK5GcA-8CbrdrFmymDF0FNvYO0/edit#gid=0) 
* [SRU (GSR) spreadsheet (Dec 16)](https://docs.google.com/spreadsheets/d/1Wt9JTEpduB0RMHHy-guL07kSh7DgHKqrXysSTuZfTaY/edit#gid=959049112)


Row {data-height=350}
-------------------------------------
### Assumptions and challenges:  


1. I currently don't allow for a selection of FTE appointment rate, and instead assume all appointments are at 50%.  
2. I assume that anyone not working over the summer applied for the hardship fund that appears to be available in this proposal, for which I assign that $1000 across the three summer months.  
3. Note that Steps 1-4 are being collapsed and Steps 9-10 are being collapsed in both proposals. Furthermore, experience based increases are only relevant up until Step 6, after which experiencebased increases don't apply.    
4. I have not been able to include the experience-based increases as well as I would like -- I am working on it. In theory we should have increases right when we pass over an experience threshold, which is not reflected here.  


Row {data-height=200}
-------------------------------------
### Contact:

If I'm missing something, please let me know:  
belwood[at]ucdavis.edu  


